\section{Interview 3}
\begin{enumerate}
    \item Yongtang Lu: Hi,how are you doing?
    \newline Pranesh: Thank you, am doing good. How about you guys?
    \item Yongtang Lu:  We are doing good, thanks. We just wanted permission to record you for the feedback of a ticket vending machine.
    \newline Pranesh: Yeah, sure. Please ask
    \item Saghana Mahesh Sarma: How often do you travel using BIXI?
    \newline Pranesh: Yes I am familiar with it, but I use it only in the summers or fall.
    \item Yongtang Lu - What is the format of the unlock code you are given when renting a bike?
    \newline Pranesh - It is a 5 digit code but they only have digits 1,2 and 3.
    \item Saghana Mahesh Sarma - Is there some way the system confirms that the Bike has been returned.
    \newline Pranesh - Yes, when you submit a bike, the docking platform’s light goes green indicating return is accepted. It is red if there is something wrong. Also, a message is sent on the app.
    \item Yongtang Lu - What happens if the station you are returning the bike to has no return platforms where you can park the bike?
    \newline Pranesh - You can request extra 15 minutes to go to the next station.
    \item Saghana Mahesh Sarma - What happens if a customer loses the unlock code?
    \newline Pranesh - You can use the terminal to get a new code issued.
    \item Yongtang Lu - But what if someone else finds it and uses it?
    \newline Pranesh - The unlock code works only for the first 5 minutes or so. After that, it does not work. So chances of that happening is very low.
    \item Saghana Mahesh Sarma - Have you ever used the membership of BIXI?
    \newline Pranesh - Actually, I generally use the membership as it is more cost effective?
    \item Saghana Mahesh Sarma - How so? How is membership more effective?
    \newline First 45 minutes are free if you are a member. So if your trips are less than 45 minutes, then you are only paying the membership cost. Also, I think we are charged less beyond that if we are member.
    \item Yongtang Lu - How does BIXI app help you ?
    \newline Pranesh - It has a map that shows stations with available bikes, icons for electric bikes and charge level. It also confirms when return is accepted. You can check out how much time has passed in your trip. Things like that. There is also a reward point system but I have no idea how it works.
    \item Saghana Mahesh Sarma: Okay Pal thank you for your feedback and providing time for giving feedback. 
\end{enumerate}


