\section{Interview 4}
\begin{enumerate}
    \item Nassrin Maarefi -Is there a time limit on how long I can keep my BIXI bike?
    \newline User - We are not supposed to keep the Bikes for more than 24 hours as it is for public use. We may incur penalties although I am not sure how much.
    \item Nassrin Maarefi - What is the mileage and speed you have seen while using Electric bike on full charge ?
    \newline User - The maximum speed I have gotten is 30 km although I haven’t tried further than that. I have travelled generally more than 5 kilometers on a full charge although I have never exhausted the battery . 
    \item Nassrin Maarefi - Do BIXI bikes have way to store items during ride?
    \newline User - Yes BIXI bikes have a basket attached to the front handle that lets you store items upto medium sized bags.
    \item Nassrin Maarefi - What are the security and safety rules that need to be followed ?
    \newline User - . We are supposed to wear helmets while we are riding the bike to conform with the general safety rules of Canada.
    \item Nassrin Maarefi - Is there any other restriction on who can use the BIXI bikes.
    \newline User - Although I have freely used the renting service as an adult, but I have heard you need a licence if the renter is between 14 to 17 years old.
    \item Nassrin Maarefi - Is there a way to reserve a bike beforehand?
    \newline User - No, I don’t think so. I have only seen bikes being taken from station when you need it.
    \item Nassrin Maarefi - Is there a period when the BIXI service is not available?
    \newline User - Yes, in last months of Winter when snow is on the roads. I think December, January you can’t. I am not sure about March and November.
    \item  Nassrin Maarefi - Can you rent for your friends?
    \newline User - Yes, you can rent multiple bikes. I think 4 is the limit, at least for the one time renting. 
    \item Nassrin Maarefi - Okay, Thank you so much for your feedback.
\end{enumerate}






