\section{Interview 2}
\begin{enumerate}
    \item Mansi: Hi,how are you doing?
    \newline Pal: I am good, how are you?
    \item Mansi: I am good thank you, May I know you name to address you?
    \newline Pal: My name is Pal sheth.
    \item Mansi: okay, hello Pal so do I have the permission to audio record you for the feedback interview of the TVM?
    \newline Pal: Yes ofcourse
    \item Mansi: Have you interacted with the TVM to buy one time passes or purchase memberships?
    \newline Pal: Yes
    \item Mansi: How often do you travel using BIXI?
    \newline Pal: Yes I use it mostly in summers twice or thrice a week to travel within 3KM range 
    \item Mansi: How often do you use the TVM for purchasing a membership/ticket?
    \newline Pal: Mostly once a month I purchase a membership 
    \item Mansi: Do you find the TVM user friendly to get all the information you need to purchase a ticket/membership?
    \newline Pal: Yes it shows me all the information related to monthly memberships and per trip costs and I would say it is a simple process of payment and accessing a bixi using access code
    \item Mansi: Does the TVM provides you the information in the language you can read?
    \newline Pal: Yes, I can read English and it does provide information in English and French
    \item Mansi: Do you think any additional information can be shown in the TVM to make the process easy?
    \newline Pal: yes I think displaying the nearest dock where the bike I need is available is an important feature you could add in case the bike is not available in current dock. This helps in case the person buying the ticket does not have access to phone.
    \item Mansi: What can be improved to ease the process of purchasing the ticket/membership?
    \newline Pal: You can create a demo video to use the system in case of people who are unfamiliar with systems like TVM
    \item Mansi: Do you think there are enough Dock/TVM in the city to purchase the ticket?
    \newline Pal: Yes I think there are a lot in my area as I live in downtown but in more towards suburbs there are very few docks, in that case providing online option would help a lot
    \item Mansi: How would you like to get the receipt of payment?
    \newline Pal: I would like to get the option of e-receipt on the email linked
    \item Mansi: How easy is the payment system in the TVM?
    \newline Pal: I usually pay with Debit/Credit so it is fine for me
    \item Mansi:  On Scale of 1-10 how much would you rate the easiness for the process of purchasing a ticket/membership?
    \newline Pal: 8
    \item Mansi: Would you also like an Online ticket buying option apart from TVM?
    \newline Pal: Yes that would be a great option to have so that prebooking can help a lot in bixi’s availability.
    \item Mansi: Would you like to have seasonal tickets?
    \newline Pal: No I use Bixi on monthly basis some months I do use it some months I skip so monthly membership works for me
    \item Mansi: Is the TVM UI user friendly or do you have any suggestion to improve it?
    \newline Pal: No I have used the TVM many time and I am easily able to purchase a ticket
    \item Mansi: Do you want notifications for getting your Pass/Ticket purchase details or trips expiring?
    \newline Pal: Yes I would definitely like to have an e-receipt for the ticket/pass purchased to keep a record
    \item Mansi: Can you provide overall rating to TVM on the scale of 1-10?
    \newline Pal: 9
    \item Mansi: Can you suggest any improvements to the TVM?
    \newline Pal: Yes, I think displaying nearby docks with available bikes can help a lot
    \item Mansi: Okay Pal thank you for your feedback and providing time for giving feedback. 
\end{enumerate}


