\section{Interview 1}
\begin{enumerate}
    \item Rishab Kumar - What happens if the Bixi dock is full?
    \newline User - We can request for a 15 mins time credit free of charge so that we may return it to some other nearby BIXI station
    \item Naman Kumar - Why would you want to rent an e-bike over a traditional bike?
    \newline User - Its easy to ride than traditional bikes ,Also I can cover larger distance over short period of time. Also , there is less physical exertion at the end of day. 
    \item Rishab Kumar - But its more costlier than traditional bikes ?
    \newline User - Yes , but it saves a lot of time , I also work as a part time food delivery worker,so its   easier for me to commute and cover the costs.
    \item Naman Kumar - How do you know if the BIXI is fully charged?
    \newline User - there will be 4 green bars on the Bixi stem which means its fully charged.
    \item Naman Kumar - Which pass do you usually opt for BIXI?
    \newline User - I usually opt for monthly pass as I use bixi very often . 
    \item Rishab Kumar - How much does it cost?
    \newline User - It costs around 20 dollars a month . it covers unlimited rides upto 45 mins.
    \item Rishab Kumar - What about after 45 mins?
    \newline User - I think its 11 cents per min after that.
    \item Rishab Kumar - Does Bixi provides any additional discounts ?
    \newline User - Yes , For concordia students , they provide 15 percent discounts on plans. 
    \item Naman Kumar - What if the Bixi that you get is defective?
    \newline User - This usually doesnt happen , but if it happens , we can leave that one to the dock and we can press the red button on docking station to notify the technician.
\end{enumerate}






